% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.

\hyphenation{Campinas}
\hyphenation{UNICAMP}


\documentclass[10pt, a4paper, roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman


\usepackage[portuguese]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}


\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'

\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

%\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.90]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\firstname{Guilherme} 
\familyname{Lucas}

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}

\mobile{+55 19 98279-1826}

\email{guilherme.slucas@gmail.com}

\begin{document}

\makecvtitle % Prints the CV title

\section{Experience}
\subsection{Professional}

\cventry{2019 -- Present}{Software Engineer}{Microsoft}{São Paulo}{Brasil}
{
}


\cventry{2018 -- 2019}{Software Engineering Intern}{Microsoft}{São Paulo}{Brasil}
{
    \begin{itemize}
        \item Developed Front and Back-End code with Python, ASP.NET Core, Java Spring and Angular.
	    \item Took care of infrastructure as code with Terraform, Docker and Kubernetes.
	    \item Worked with the team to design and implement Distributed Cloud Applications with Azure.
	    \item Focus on the best engineering practices like CI, CD, testing, DevOps, monitoring, etc.
    \end{itemize}
Skills: C\#, Azure, Docker, Angular, Python, Terraform, Kubernetes, Java.
}

\cventry{2017 -- 2018}{Data Science Intern}{CETAX}{São Paulo}{Brasil}
{
    \begin{itemize}
        \item Development of big data applications, writing API's to obtain data and creating Machine Learning models. 
        \item Helped the implementation of code review culture.
    \end{itemize}
    Skills: Python, Django, Spark and GNU/Linux Systems.
}

\subsection{Academic}
\cventry{2016 -- 2017}{Undergraduate Research}{IBM - Unicamp}{Campinas}{Brasil}
{
    \begin{itemize}
        \item Developed \href{https://github.com/Guilhermeslucas/powergraph}{PowerGraph}, a monitoring software for a cloud server used by hundreds of people.
        \item Wrote several code to automate GNU/Linux machines deploys, in \href{https://github.com/Guilhermeslucas/Ansible-Code}{Ansible} and 
            \href{https://github.com/Guilhermeslucas/Dockerfiles}{Docker}.
        \item Wrote \href{http://openpower.ic.unicamp.br/blog/}{texts e tutorials}, read by people all over the world. 
    \end{itemize}
    Skills: C/C++, Python, Shell Script, Ansible, Docker and GNU/Linux Systems.
}
\subsection{Volunteer}
\cventry{2017 -- 2018}{Member}{LivreCamp - Unicamp}{Campinas}{Brasil}
{
    Worked as assistant and teacher on Shell Script and GNU/Linux courses.
}
\cventry{2016 -- 2016}{Teaching Assistant}{Programa de Auxílio Discente}{Campinas}{Brasil}
{
    Applied the pratical tests, corrected exercises and helped 60 students with questions for Digital Circuits Subject.
}
\cventry{2015 -- 2016}{Undergraduate Representative}{Institute of Computing - Unicamp}{Campinas}{Brasil}
{ 
    Dealing with money investiment and infrastructure affairs for the whole Institue of Computing.
}
\cventry{2014 -- 2015}{Organizing Committee}{Computing Week Unicamp (SECOMP)}{Campinas}{Brasil}
{
    Increased income by 85\% and conference participants by more than 50\%, reaching 280 people.
}
\cventry{2014 -- 2016}{Vice President}{CACo - Centro Acadêmico de Computação}{Campinas}{Brasil}
{
}
\section{Education}

\cventry{2014 -- 2018}{Computer Engineering}{University of Campinas (UNICAMP)}{Campinas}{Brasil}
{
    \begin{itemize}
        \item Helped to implement a software that helps students choosing their subjects, with Python and Django.
        \item Won third place at Microsoft Hack the Campus Hackaton, with a chat bot that analyses university data.
    \end{itemize} 
}

\section{Languages}

\cvitemwithcomment{Native}{Portuguese}{}
\cvitemwithcomment{Fluent}{English}{}
\cvitemwithcomment{Basic}{Spanish}{}
\cvitemwithcomment{Basic}{French}{}

\section{Technical Skills}

\cvitem{Intermediate}{C\#, \LaTeX, HTML, CSS, Docker, Ansible, Angular, Kubernetes, Terraform}
\cvitem{Good}{Python, C/C++, Shell Script, Git, GNU/Linux Operational Systems, Lisp}
\end{document}
